\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fontawesome}

\hypersetup{
    colorlinks=true,
    linkcolor=black,
    urlcolor=black,
}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{12pt}{8pt}

% Remove page numbers
\pagestyle{empty}

\begin{document}

\begin{center}
    {\LARGE\bfseries Arnold Roy Nazareth}\\[8pt]
    \faPhone\ +61-0433842433 \quad
    \faEnvelope\ arnoldnazareth8@gmail.com \quad
    \faLinkedin\ linkedin.com/in/arnold-nazareth-5738351a9
\end{center}

\section{Professional Objective}
\begin{itemize}[leftmargin=*]
    \item A dedicated and detail-oriented professional seeking employment as a python developer, database analyst, data scientist, machine learning engineer.
    \item Adept at delivering exceptional customer service while upholding the highest standards of efficiency and professionalism.
    \item Demonstrates the ability to thrive in fast-paced environments while ensuring operational accuracy and service excellence.
    \item Committed to maintaining workplace employment standards, organization, and fostering a collaborative team environment.
    \item Core competencies: Adaptability, communication, time management, critical thinking, and interpersonal skills.
\end{itemize}

\section{Professional Experience}

\noindent
\textbf{Pancake Parlour, Victoria, Australia} \hfill \textbf{Nov 2025 -- Present}\\
\textit{Baker}
\begin{itemize}[leftmargin=*]
    \item Prepare high-quality batter and baked goods, ensuring consistency and adherence to Pancake Parlour's standards while managing multiple baking stations during peak service hours.
    \item Execute quality control procedures and manage inventory levels, monitoring stock rotation, ordering supplies, and minimizing waste to maintain optimal kitchen operations.
    \item Deliver exceptional customer service by engaging with patrons, addressing inquiries, and ensuring a positive dining experience while maintaining professional kitchen standards.
    \item Collaborate with kitchen team members to coordinate workflow, support training initiatives, and maintain efficient operations during high-volume service periods.
\end{itemize}

\noindent
\textbf{Chromagen, Redwood Dr, Victoria} \hfill \textbf{Apr 2025 -- Aug 2025}\\
\textit{Retail Admin}
\begin{itemize}[leftmargin=*]
    \item Key tools used: MS Excel, SAP Business one, Python, Dropbox, Canva.
    \item I was responsible for paperwork related to the filing of rebates for hot water systems installed in New South Wales.
    \item In addition to the job description to improve speed, I implemented workflows on python to help automate certain repeating tasks like file management (creation and deletion of files, renaming files, saving file paths to excel).
\end{itemize}

\noindent
\textbf{Oracle-Cerner, Bangalore, Karnataka} \hfill \textbf{Aug 2022 -- Feb 2025}\\
\textit{Systems Analyst - 1}
\begin{itemize}[leftmargin=*]
    \item Implemented and managed enterprise solutions, including SAP Business Objects, IBM WebSphere, IBM MQ, Jira and proprietary internal tools, to ensure seamless integration and operational efficiency.
    \item Collaborated with cross-functional teams to provide high-quality technical support to hospitals worldwide, facilitating uninterrupted healthcare services.
    \item Deployed and maintained solutions on both remote and client-hosted servers, ensuring optimal performance, scalability, and security compliance.
    \item Led a team in the execution of multiple projects in alignment with client specifications, facilitating a seamless go-live experience and ensuring timely project delivery.
    \item Conducted system performance evaluations and troubleshooting to optimize software efficiency, reduce downtime, and improve user experience.
    \item Coordinated with stakeholders and technical teams to streamline workflows, improve implementation strategies, and ensure alignment with business objectives.
    \item Developed technical documentation and training materials that enable teams to efficiently manage deployed solutions and reduce the time to on-boarding new team members.
\end{itemize}

\noindent
\textbf{Nife Labs, Bangalore, Karnataka} \hfill \textbf{Dec 2020 -- Mar 2021}\\
\textit{AI Intern}
\begin{itemize}[leftmargin=*]
    \item Worked on Accelerating an AI models inference with Cudnn and TensorRT.
    \item Reduced the inference time of an AI model by 25 percent on predicting a class of an image.
\end{itemize}

\section{Academic Qualifications}

\noindent
\textbf{Monash University} \hfill \textbf{Mar 2025 -- Dec 2026}\\
\textit{Master of Artificial Intelligence (Expected)}
\begin{itemize}[leftmargin=*]
    \item Actively engaged in academic and extracurricular activities, including professional networking events, technical workshops, and university sports clubs.
\end{itemize}

\noindent
\textbf{Christ (Deemed to be) University} \hfill \textbf{Jun 2018 -- Jun 2022}\\
\textit{Bachelor of Engineering in Electronics and Communication}
\begin{itemize}[leftmargin=*]
    \item Achieved academic distinction with an Honors specialization in Intelligent Systems.
\end{itemize}

\noindent
\textbf{Kensri School} \hfill \textbf{May 2016 -- Apr 2018}\\
\textit{Higher Secondary Education}
\begin{itemize}[leftmargin=*]
    \item Specialized in Physics, Chemistry, Computer Science, and Mathematics.
\end{itemize}

\noindent
\textbf{Kensri School} \hfill \textbf{Apr 2016}\\
\textit{Secondary Education}

\end{document}
